Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-22 tex/paper1/paper1.tex
edits to the paper

All these detections algorithms, and many detections in the literature
make either the explicit or implicit assumption that the observed
time-series consists of a background trend of some kind and
(approximately) Gaussian-distributed noise which must be taken in to
account in order to test for the presence of an oscillatiory signal.
{\bf The aim of this paper is to investigate the nature of the Fourier
  power spectrum in regions of interest to coronal seismology, to look
  for evidence that the above assumption is appropriate.  Data from
  the Atmospheric Imaging Assembly (AIA,
  \citealp{2012SoPh..275...17L}) on board the Solar Dynamics
  Observatory (SDO, \citealp{2012SoPh..275....3P}) is used.  It is
  shown that time-series of coronal emission have power-law power
  spectra, at least approximately.}  The \PL\ \PS\ nature of coronal
emission has implications for coronal seismology, and may be
indicative of the nature of the fundamental energy deposition that
keeps the corona hot.

@@

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figure \ref{fig:loc171193} shows the location of the regions on sample
images from the time range considered. {\bf These locations, selected
  by visual inspection, were chosen because they are representative of
  commonly observed structures in the corona.  In addition,
  oscillatory power has been identified previously over sunspots and
  loop footpoints \citep{2002A&A...387L..13D} and moss structures
  \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
  for comparison.}

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
  in the y-direction, in heliocentric cartesian co-ordinates.  The
  images show NOAA AR 1575 and some surrounding area.
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

@@

Table \ref{tab:parameters} gives the parameter estimates and 68\%
credible intervals of the parameter values for model $M_{2}$, {\bf the
  maximum value of the ratio $G(\nu)/P_{1}(\nu)$ and its location}.
The power law indices for all regions and both wavebands lie in the
range 1.8 to 2.3, although there is no consistency between one
waveband and another.  For example, the 171\AA\ and 193\AA\ loop
footpoint results both have the same power law index, but the other
regions do not.  However, it should be noted that there is no {\it a
  priori} reason why the power law indices for a region seen in two
different wavebands should be the same.  This is because each waveband
is designed to examine different features on the Sun in broadly
different temperature ranges, and may be imaging very different
physical processes: hence, the emission seen in one waveband need not
have the same statistical properties as any other.

@@

\section{Conclusions}\label{sec:conc}

Time series of AIA 171\AA\ and 193\AA\ images show approximately power
law like properties {\bf in four representative regions} of the
corona.  {\bf It has been shown that the detection of narrow band
  oscillatory power in the practice of coronal seismology must take in
  to account the presence of the \PL\ like \PS.  Detection thresholds
  should also increase in order to reduce the number of false positive
  detections in the presence of \PL\ like \PS.} The power spectra have
been modelled using three components: a \PL\ \PS, a lognormal
component, and a constant background.  It is hypothesized that the
power-law component is due to the sum along the line of sight of a
large number of statistically similar energy deposition events.  It is
also hypothesized that the lognormal component is due a combination of
the channeling of oscillatory power from lower to higher levels of the
solar atmosphere and lower temperature emission lines in the AIA
171\AA\ and 193\AA\ bandpasses.

Future studies will include examining power spectra at many more
locations on and off the disk, as well as using the AIA 355\AA, 94\AA,
131\AA and 211\AA\ wavebands.  The power-law index in individual
pixels will also be determined, and correlated with other physical
quantities such as the emission from those pixels.  Finally, a better
understanding of the source of the power-law power spectrum will come
from comparing the \Fps\ of simulated observations to the \Fps\ of the
data in all the AIA wave-bands that are sensitive to higher
temperatures.  This will bring new constraints on the simulations and
improve our understanding of the temporal behavior of the solar
corona.

@@

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\citealp*{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma_{j}^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$, $N_{f}$
is the number of Fourier frequencies, and $\sigma_{j}$ is the normal
distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution (except
$N_{eff}$), and are given in Table \ref{tab:priors}.  Each MCMC chain
that was run took 100,000 samples, with burn-in assumed to be at
50,000 samples.  The chain is thinned by taking every fifth element in
the chain, forming the final sample from which the parameter estimates
and their uncertainties are calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1 and 2} &
\colhead{Model 2 only} \\
}
\startdata
$\log_{10} A$ & $-4.34 \rightarrow 2.00$  & {\it not applicable} \\
$n$ & $1\rightarrow 6$ & {\it not applicable}  \\
$\log_{10} C$ & $-8.68 \rightarrow 2.00$ & {\it not applicable} \\
$\log_{10} \alpha$  & {\it not applicable}  & $8.68 \rightarrow -1.00$ \\
$\beta$ & {\it not applicable} & $0.1 - 10$ (mHz) \\
$\log_{10}\delta$ & {\it not applicable} & $0.00 \rightarrow 3.00$ \\
\enddata
\end{deluxetable}
The \mFpa\ are assumed to
be normally distributed with a width given by $\sigma_{mean}$ as
calculated above.  A five step fitting process is used to fit Models 1
and 2 to the data, and is described below.

\begin{enumerate}
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by the priors for $A$, $n$ and $C$ (Table
  \ref{tab:priors}).  The MCMC sampler is run to fit Model 1, assuming
  $\sigma_{j} = \sigma_{original, j}$ the width of the distribution of
  Fourier power at frequency $G(\nu_{j})$.  Since the widths
  $\sigma_{original, j}$ are large it allows the fitting algorithm to
  converge to an approximate fit solution.
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by the priors for $A$, $n$, and $C$
  (Table \ref{tab:priors}).  The MCMC sampler is run to fit Model 1 with
  $\sigma_{j} = \sigma_{original, j}/sqrt{N_{eff}}$, seeded with
  estimated parameter values from step 1.  This generates a better
  estimate to the parameters of the model fit.  The resulting
  parameter estimates are given by the mean values of marginal
  probability distribution functions, and are the final estimates for
  Model 1.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.  This is done by
  (least-squares) fitting $G(\nu)$ to the positive residuals in the
  frequency range 0.1 - 10 mHz.
\item The MCMC sampler is run to fit Model 2 assuming $\sigma_{j} =
  \sigma_{original, j}$, seeded with the mean parameter values of
  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
  step 3.
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by all the priors for Model 2 (Table \ref{tab:priors}).
  The MCMC sampler is run to fit Model 2 with $\sigma_{j} =
  \sigma_{original, j}/\sqrt{N_{eff}}$, seeded with estimated
  parameter values from step 4.  The resulting parameter estimates are
  given by the mean values of marginal probability distribution
  functions, and are the final estimates for Model 2.
\end{enumerate}
Models are selected using the Akaike Information Criteria
\citep{2007MNRAS.377L..74L}, as described in the main text.
Conveniently, the AIC is calculated by the PyMC package used to
perform the MCMC sampling.  The 68\% credible intervals for the model
parameters are quoted in Table \ref{tab:parameters}.  The upper and
lower limits to the credible intervals are found by determining the
values beyond which 16\% of the probability lies in each wing of the
marginal distributions.

>>>>

All these detections algorithms, and many detections in the literature
make either the explicit or implicit assumption that the observed
time-series consists of a background trend of some kind and
(approximately) Gaussian-distributed noise which must be taken in to
account in order to test for the presence of an oscillatiory signal.
{\bf However, two recent papers cast doubt on this assumption.
  \cite{2014AA...563A...8A} integrate emission over small portions of
  active regions and the quiet Sun as seen in the 19.5 nm passband
  images from EIT and show that the resulting time-series has an
  approximate \PL\ \Fps\ over the frequency range 0.01 - 1 mHz.
  \citet{gupta2014} showed \PL\ \PA\ in the intensity at six single
  points in AIA 171 coronal plumes extending over the frequency range
  $0.3\rightarrow 4.0$ mHz.}  {\bf The aim of this paper is to
  investigate the nature of the Fourier power spectrum in regions of
  interest to coronal seismology, to look for evidence that the above
  assumption is appropriate.  Data from the Atmospheric Imaging
  Assembly (AIA, \citealp{2012SoPh..275...17L}) on board the Solar
  Dynamics Observatory (SDO, \citealp{2012SoPh..275....3P}) is used.
  It is shown that time-series of coronal emission have power-law
  power spectra, at least approximately.}  The \PL\ \PS\ nature of
coronal emission has implications for coronal seismology, and may be
indicative of the nature of the fundamental energy deposition that
keeps the corona hot.

@@

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figure \ref{fig:loc171193} shows the location of the regions on sample
images from the time range considered. {\bf These locations, selected
  by visual inspection, were chosen because they are representative of
  commonly observed structures in the corona.  Further,
  oscillatory power has been identified previously over sunspots and
  loop footpoints \citep{2002A&A...387L..13D} and moss structures
  \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
  for comparison.}
\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
  in the y-direction, in heliocentric cartesian co-ordinates.  The
  images show NOAA AR 1575 and some surrounding area.
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

@@

Table \ref{tab:parameters} gives the parameter estimates and 68\%
credible intervals of the parameter values for model $M_{2}$, {\bf the
  maximum value of the ratio $G(\nu)/P_{1}(\nu)$ and its location}.
The power law indices for all regions and both wavebands lie in the
range 1.8 to 2.3, although there is no consistency between one
waveband and another.  For example, the 171\AA\ and 193\AA\ loop
footpoint results both have the same power law index, but the other
regions do not.  However, it should be noted that there is no {\it a
  priori} reason why the power law indices for a region seen in two
different wavebands should be the same.  This is because each waveband
is designed to examine different features on the Sun in broadly
different temperature ranges, and may be imaging {\bf different parts
  of the same temperature-dependent physical process.  Also,
  line-of-sight effects may be different in different wavebands (and
  locations).}  Hence, the emission seen in one waveband need not have
the same statistical properties as any other.

@@

\section{Conclusions}\label{sec:conc}
Time series of AIA 171\AA\ and 193\AA\ images show approximately power
law like properties {\bf in four representative regions} of the
corona.  {\bf It has been shown that the detection of narrow band
  oscillatory power in the practice of coronal seismology must take in
  to account the presence of the \PL\ like \PS.  Detection thresholds
  should also increase in order to reduce the number of false positive
  detections in the presence of \PL\ like \PS.} The power spectra have
been modelled using three components: a \PL\ \PS, a lognormal
component, and a constant background.  It is hypothesized that the
power-law component is due to the sum along the line of sight of a
large number of statistically similar energy deposition events.  It is
also hypothesized that the lognormal component is due a combination of
the channeling of oscillatory power from lower to higher levels of the
solar atmosphere and lower temperature emission lines in the AIA
171\AA\ and 193\AA\ bandpasses.

Future studies will include examining power spectra at many more
locations on and off the disk. {\bf Automated definitions of coronal
  structures will be used to segment particular coronal features from
  the data, and so provide improved information of the differences the
  coronal structure makes to the observed \PL\ \PS.  Other AIA
  wavebands, such as AIA 355\AA, 94\AA, 131\AA and 211\AA\ will be
  used to look for further evidence of \PL\ \PA\ in different broad
  temperature ranges in the solar corona.}  The power-law index in
individual pixels will also be determined, and correlated with other
physical quantities such as the emission from those pixels.  Finally,
a better understanding of the source of the power-law power spectrum
will come from comparing the \Fps\ of simulated observations to the
\Fps\ of the data in all the AIA wave-bands that are sensitive to
higher temperatures.  This will bring new constraints on the
simulations and improve our understanding of the temporal behavior of
the solar corona.

@@

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\citealp*{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma_{j}^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$, $N_{f}$
is the number of Fourier frequencies, and $\sigma_{j}$ is the normal
distribution width at frequency $\nu_{j}$.  {\bf Each of the priors
  for the parameters in each model has a uniform distribution, and are
  given in Table \ref{tab:priors}.  For some parameters, the logarithm
  of the model parameter has a uniform distribution, which aids in the
  exploration of parameter space}.  Each MCMC chain that was run took
100,000 samples, with burn-in assumed to be at 50,000 samples.  The
chain is thinned by taking every fifth element in the chain, forming
the final sample from which the parameter estimates and their
uncertainties are calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1 and 2} &
\colhead{Model 2 only} \\
}
\startdata
$\log_{10} A$ & $-4.34 \rightarrow 2.00$  & {\it not applicable} \\
$n$ & $1\rightarrow 6$ & {\it not applicable}  \\
$\log_{10} C$ & $-8.68 \rightarrow 2.00$ & {\it not applicable} \\
$\log_{10} \alpha$  & {\it not applicable}  & $8.68 \rightarrow -1.00$ \\
$\beta$ & {\it not applicable} & $0.1 - 10$ (mHz) \\
$\log_{10}\delta$ & {\it not applicable} & $0.00 \rightarrow 3.00$ \\
\enddata
\end{deluxetable}
The \mFpa\ are assumed to
be normally distributed with a width given by $\sigma_{mean}$ as
calculated above.  A five step fitting process is used to fit Models 1
and 2 to the data, and is described below.

\begin{enumerate}
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by the priors for $A$, $n$ and $C$ (Table
  \ref{tab:priors}).  The MCMC sampler is run to fit Model 1, assuming
  $\sigma_{j} = \sigma_{original, j}$ the width of the distribution of
  Fourier power at frequency $G(\nu_{j})$.  Since the widths
  $\sigma_{original, j}$ are large it allows the fitting algorithm to
  converge to an approximate fit solution.
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by the priors for $A$, $n$, and $C$ (Table
  \ref{tab:priors}).  The MCMC sampler is run to fit Model 1 with
  $\sigma_{j} = \sigma_{original, j}/sqrt{N_{eff}}$, seeded with
  estimated parameter values from step 1.  This generates a better
  estimate to the parameters of the model fit.  The resulting
  parameter estimates are given by the mean values of marginal
  probability distribution functions, and are the final estimates for
  Model 1.  The reduced chi-squared measurement $\chi^{2}_{r}$ for
  model $M_{1}$ is calculated using the values of $\sigma_{j}$ above.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.  This is done by
  (least-squares) fitting $G(\nu)$ to the positive residuals in the
  frequency range 0.1 - 10 mHz.
\item The MCMC sampler is run to fit Model 2 assuming $\sigma_{j} =
  \sigma_{original, j}$, seeded with the mean parameter values of
  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
  step 3.
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by all the priors for Model 2 (Table
  \ref{tab:priors}).  The MCMC sampler is run to fit Model 2 with
  $\sigma_{j} = \sigma_{original, j}/\sqrt{N_{eff}}$, seeded with
  estimated parameter values from step 4.  The resulting parameter
  estimates are given by the mean values of marginal probability
  distribution functions, and are the final estimates for Model 2.
  The reduced chi-squared measurement $\chi^{2}_{r}$ for model $M_{2}$
  is calculated using the values of $\sigma_{j}$ above.
\end{enumerate}
{\bf The preferred model is selected using the Akaike Information
  Criteria \citep{2007MNRAS.377L..74L}, as described in the main
  text.}  Conveniently, the AIC is calculated by the PyMC package used
to perform the MCMC sampling.  The 68\% credible intervals for the
{\bf parameters of the model preferred using the AIC} are quoted in
Table \ref{tab:parameters}.  The upper and lower limits to the
credible intervals are found by determining the values beyond which
16\% of the probability lies in each wing of the marginal
distributions.
